Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-10-21 thesis/paper_draft.qmd
codes for by level plot in tourism

![Percentage relative improvement in Winkler score at 95% nominal coverage by level (left), and empirical coverage of 95% prediction intervals by level (right)](D:/Github/Recon_Honours_Thesis/figs/tourism_coverage_95.png){#fig-tourism-coverage-95-level}

>>>>

<!-- ![Percentage relative improvement in Winkler score at 95% nominal coverage by level (left), and empirical coverage of 95% prediction intervals by level (right)](D:/Github/Recon_Honours_Thesis/figs/tourism_coverage_95.png){#fig-tourism-coverage-95-level} -->

```{r}
#| label: fig-tourism-coverage-95-level
#| fig-cap: "Percentage relative improvement in Winkler score at 95% nominal coverage by aggregation level (left), and empirical coverage of 95% prediction intervals by aggregation level (right)."
#| fig.height: 12
#| fig.width: 9
#| out.width: "100%"

tourism_coverage95 <- readRDS(paste0(path, "/thesis/lib/tourism_coverage95.rds"))
tourism_W95_level <- readRDS(paste0(path, "/thesis/lib/tourism_W95_level.rds"))

p_c95_lvl <- tourism_coverage95 |> 
  group_by(level, .model) |> 
  summarise(mean_coverage = mean(coverage)) |> 
  encode_recon_models() |> 
  ggplot(aes(x = model_label, y = mean_coverage, fill = family, alpha = pc_k)) +
    geom_col(color = "black") +
    scale_alpha_manual(values = c("0" = 1, "1" = 0.7, "2" = 0.4), guide = "none") +
    labs(x = "", y = "Empirical Coverage",
         title = "Empirical coverage of 95% prediction intervals by level") +
    geom_hline(yintercept = 0.95, linetype = "dashed", color = "black") + # draw line for coverage
    facet_wrap(~ level, ncol=2, scales = "free_y") +
    recon_fill_scale +
    theme_minimal() +
    # rotate the x axis labels
    theme(axis.text.x = element_text(angle = 20, hjust = 0.5))

p_W95_lvl <- tourism_W95_level |> 
  ggplot(aes(x = model_label, y = pct_change, fill = family, alpha = pc_k)) +
    geom_col(color = "black") +
    scale_alpha_manual(values = c("0" = 1, "1" = 0.7, "2" = 0.4), guide = "none") +
    labs(x = "", y = "% improvements",
         title = "Winkler score 95% by level") +
    facet_wrap(~ level, ncol=2, scales = "free_y") +
    recon_fill_scale  +
    guides(fill = "none") +
    theme_minimal() +
    # rotate the x axis labels
    theme(axis.text.x = element_text(angle = 20, hjust = 0.5))

p_W95_lvl + p_c95_lvl +
  plot_layout(ncol = 1, guides = "collect", axis_titles = "collect") &
  theme(legend.position = "right", legend.direction = "vertical", legend.title.position = "top")
```
